Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 report/report.tex
Halfway through chapter 4
Added ethics form
Added stub conference paper to use in appendix
Abstract... done?

\title{Improving content discovery through combining linked data and data mining techniques}
\author{Ross Fenning}

@@

\maketitle
\tableofcontents

\input{chapters/01-intro}
\input{chapters/02-background}
\input{chapters/03-design}

\chapter{Implementation}
\label{chp:implementation}

\chapter{Evaluation}
\label{chp:evaluation}

\chapter{Conclusion}

@@

>>>>

\title{Improving content discovery through combining linked data and data mining techniques}
\author{\vfill\textbf{Ross Fenning}}
\affil{
\vfill
  Dissertation submitted in partial fulfilment of the
\\
requirements for the degree of
\\
Master by Advanced Study in Software Engineering and Internet Architecture

\vfill

\textbf{School of Electrical Engineering \& Computer Science}
\\
\textbf{University of Bradford}
\vfill
}

@@

\maketitle

\begin{abstract}
MSc in Software Engineering and Internet Architecture 2016

Improving content discovery through combining linked data and data mining techniques

By Ross Fenning

Project Supervisor: Dr. D. Thakker

An comparative study of multiple approaches for extracting linked data
from web content published by the BBC for the purposes of applying
machine learning to cluster related content.

This project designs and implements a process by which semantic data
about any piece of online media content can be extracted into RDF
models in
multiple ways and feature
sets for machine learning can be generated from
that data. The clusters produced by fourteen different permutations
of techniques are evaluated and a potential application of suggesting
related content is mocked up for qualititative evaluation.

It is concluded organisations can very easily make use of
embedded semantics within web pages due to better semantic properties
being made available in recent years because of pressure from
social media sites such as Facebook and Twitter.
These embedded semantics provide a good baseline for simple
learning that can group content based on broad categorisation.

However, feedback from the evaluation suggests that real value for
users from suggesting related content will come from linking items
based on topics and themes, which are better found via entity
extraction systems such as DBPedia Spotlight.

A simple application of entity extraction shows promising results in
evaluation and is highlighted as an area for organisations to explore
tuning to provide a powerful complement to embedded semantics.

\end{abstract}

\tableofcontents

\input{chapters/01-intro}
\input{chapters/02-background}
\input{chapters/03-design}
\input{chapters/04-implementation}
\input{chapters/05-analysis}
\input{chapters/06-evaluation}
\input{chapters/07-conclusions}

@@

\appendix

\chapter{Proposal}
\chapter{Ethics Form}
\includepdf[pages=1-4]{ethics.pdf}
\chapter{Summary}
